%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Umer936 Resume
% XeLaTeX 
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/
% 
% CV of:
% Umer Salman (umer936@gmail.com)
% https://github.com/umer936/My-CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage[super]{nth} 
\usepackage{lastpage}
\usepackage{fancyhdr}
\long\def\/*#1*/{} 
\pagestyle{fancy}
\fancyhf{} % to clear existing header/footer if you don't want it
\renewcommand\headrulewidth{0pt}

\begin{document}
\header{umer}{salman}{\noindent\rule{10cm}{0.4pt}} % Your name and current job title/field
\rfoot{\thepage\ of \pageref{LastPage}}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
7210 Hovingham 
San Antonio, TX 78257
USA 
~
(936) 463 8626
~
\href{mailto:umer936@gmail.com}{umer936@gmail.com}
\href{mailto:umer936@umer936.com}{umer936@umer936.com}
\href{http://umer936.com}{umer936.com}
\href{http://facebook.com/Umer936}{fb://Umer936}
\href{http://google.com/+umersalman}{google/+umersalman}
~ 
\section{programming}
CSS3 \& HTML5 
PHP ({\color{red} $\varheartsuit$} Laravel) 
MySQL 
JavaScript, CoffeeScript  
jQuery 
Java, C++ 
\LaTeX \ (this r\'esum\'e)
Ruby, Python 
TIBASIC 
Git, SVN, Mercurial 
~
\section{operating systems}
Linux 
Android 
OS X 
iOS 
Windows 
BSD 
~ 
\section{software skills}
Basic SolidWorks 
CyberLink PowerDirector 
Eclipse 
Android Studio 
Paint.NET 
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{high school}

\begin{entrylist}

%------------------------------------------------

\entry
{2013--Now}
{\nth{10}-\nth{12} {\normalfont grade}}
{TMI - The Episcopal School of Texas}
{Continued high school in San Antonio, Texas}

%------------------------------------------------

\entry
{2012--2013}
{\nth{9} {\normalfont grade}}
{Saint Andrew's Episcopal School}
{Began high school in Jackson, Mississippi}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\/*

\subsection{Full Time}

\begin{entrylist}

%------------------------------------------------

\entry
{2012--Now}
{LEHMAN BROTHERS}
{Los Angeles, California}
{\emph{1\textsuperscript{st} Year Analyst} \\
Developed spreadsheets for risk analysis on exotic derivatives on a wide array of commodities (ags, oils, precious and base metals), managed blotter and secondary trades on structured notes, liaised with Middle Office, Sales and Structuring for bookkeeping. \\
Detailed achievements:
\begin{itemize}
\item Learned how to make amazing coffee
\item Finally determined the reason for \textsc{PC LOAD LETTER}:
\begin{itemize}
\item Paper jam
\item Software issues:
\begin{itemize}
\item Word not sending the correct data to printer
\item Windows trying to print in letter format
\end{itemize}
\item Coffee spilled inside printer
\end{itemize}
\item Broke the office record for number of kitten pictures in cubicle
\item Learned how to make more amazing coffee on a new machine
\end{itemize}}

%------------------------------------------------

\end{entrylist}

*/ 

% \subsection{work}

\begin{entrylist}

\entry
{2012-Now}
{Ingress (Niantic, Inc.)}
{}
{\emph{Regional Moderator} \\ 
Ingress is a game made by Google where the entire world is the playing field shared by 2 teams. Thus, coordination on a global scale must occur. 
	\begin{itemize}
	\item Created and manage the South Texas roster website 
	\begin{itemize}
		\item \href{http://satxresist.com}{satxresist.com}
	\end{itemize}
	\item Improved the usability of Google's web app by JavaScript bookmarklets for thousands of users 
	\item Manage cross-team affairs to ensure safe play for all 
	\item Oversee operations that span multiple continents 
	\item Directly communicate with hundreds of others to facilitate operations 
	\end{itemize}
	}


\entry
{2011-Now}
{Socialcu.be}
{}
{\emph{Developer, Administrator, and Moderator} \\
Developed a social networking platform that is home to thousands of users}

%------------------------------------------------

\entry
{2015}
{Parlevel Systems}
{San Antonio, Texas}
{\emph{Summer Intern} 
	\begin{itemize}
	\item Worked on the development of analytical software for vending machine operators in North America 
	\item Developed the company's foray into micromarkets 
	\begin{itemize}
		\item Generates roughly \$50/day per location 
	\end{itemize}
	\item Created web tools to allow the company itself to run more efficiently
	\end{itemize}
	}

%------------------------------------------------

\entry
{2014}
{Tots N Teens Pediatric Urgent Care}
{San Antonio, Texas}
{\emph{Logo Creator and Website Manager} \\
	Created the logo for a local urgent care clinic}

%------------------------------------------------

\entry
{2014}
{Umer936}
{San Antonio, Texas}
{\emph{Website Builder} \\
	Built professional websites for businesses and clients by employing my knowledge of web development}

%------------------------------------------------
	
\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{certifications}

\begin{entrylist}

%------------------------------------------------

\entry
{2013}
{Certification of Graduate-Level Course}
{Royal Holloway University of London}
{Graduated an online course titled "Malicious Software and its Underground Economy: Two Sides to Every Story." The course was about traditional and mobile security threats and the underground ecosystem that drives the illegal, yet profitable, business.}

%------------------------------------------------

\end{entrylist} 

\section{awards}

\begin{entrylist}

%------------------------------------------------

\entry
{2014-Now}
{National Honors Society}
{TMI - The Episcopal School of Texas}
{Honors students who display excellence in scholarship, leadership, service, and character.}

%------------------------------------------------

\entry
{2013}
{Erasmus Award}
{Saint Andrew's Episcopal School}
{Awarded to the student that is most driven and most excited about learning.}

%------------------------------------------------

\end{entrylist}

\section{extracurriculars}

\begin{entrylist}

%------------------------------------------------

\entry
{2014-Now}
{Quiz Bowl}
{TMI - The Episcopal School of Texas}
{Compete with other schools in trivia in all academic subjects.}

%------------------------------------------------

\entry
{2013-2014}
{Track and Field}
{TMI - The Episcopal School of Texas}
{Competed in 400m and 800m events at various Texas meets.}

%------------------------------------------------

\entry
{2013}
{Science Bowl}
{Saint Andrew's Episcopal School}
{Competed with schools in various science subjects.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{projects}

\begin{entrylist}

%------------------------------------------------

\entry
{2012-Now}
{Android}
{San Antonio, Texas}
{Contributed to Android in many ways 
\begin{itemize}
	\item Software
	\begin{itemize} 
		\item Created ROMs for the HTC One X and OnePlus One (adb/fastboot)  
		\item Built an app to allow phone/tablet to function as a \nth{2} monitor for a computer
		\item Made scripts for a phone to function as a smartwatch (WiFi, Bluetooth)
		\item Named a Snapchat filter 
	\end{itemize} 
	\item Hardware 
	\begin{itemize}
		\item Built an IR blaster 
		\item Created a wireless charger for HTC One X 
	\end{itemize}
\end{itemize}
}

%------------------------------------------------

\entry
{2013}
{Simple Source Viewer}
{San Antonio, Texas}
{Simple, easy to use app for Windows 8, RT, 8.1, and 10 to allow viewing of the source code of a webpage.}

%------------------------------------------------

\entry
{2013}
{Chromecast}
{San Antonio, Texas}
{Discovered additional tools to expand the potential of the \$35 device. Findings were published on ReadWriteWeb, XDA Developers, and other tech sites.}

%------------------------------------------------

\entry
{2013}
{CygwinHere}
{San Antonio, Texas}
{Cygwin is a Windows CMD mod to bridge CMD and a Linux Terminal. My CygwinHere registry tweak ports over the "Open in Terminal" function.}

%------------------------------------------------

\entry
{2012-2014}
{ExtempEngine}
{San Antonio, Texas}
{ExtempEngine was a Chrome App to automatically download and sort articles from news sources around the world. This allowed easy access to those sources during an extemporaneous debate round without having an internet connection.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	ROBOTICS SECTION
%----------------------------------------------------------------------------------------

\section{robotics}

\begin{entrylist}

%------------------------------------------------

\entry
{2015}
{FIRST Robotics Competition}
{Brandeis High School}
{\color{red}Type about FRC \\ This needs a bullet \\ point \\ list \\ (svn, gcc)}

%------------------------------------------------

\entry
{2015}
{FIRST Tech Challenge}
{TMI - The Episcopal School of Texas}
{\color{red}Type about FTC \\ This might need \\ one \\ too \\ so I can push \\ the next section \\ off the page}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	SPEECH AND DEBATE SECTION
%----------------------------------------------------------------------------------------

\section{speech and debate}

\begin{entrylist}

%------------------------------------------------

\entry
{2012-2013}
{Policy Debate}
{Saint Andrew's Episcopal School}
{Qualified and competed at NCFL Nationals for CX debate. Also competed at colleges, including Harvard and Mississippi State.}

%------------------------------------------------

\entry
{2012-2013}
{International Extemporaneous}
{Saint Andrew's Episcopal School}
{Prepared and delivered 7 minute speeches regarding international affairs. Ranked highly at every competition.}

%------------------------------------------------

\entry
{2012-2013}
{Congress}
{Saint Andrew's Episcopal School}
{Competed in mock Congressional debate.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{other skills and interests}

\textbf{professional:} coding, programming, creating, web design, web app creation, software design, building, wiring, computer software, tech 
\\ 
\textbf{personal:} puzzles, math, gaming (League of Legends), listening to others (7cupsoftea.com), computer hardware, reading (science and mistery books)   \\ 
\textbf{languages:} conversant in Urdu, Spanish semi-fluency, can read Arabic and Greek

\end{document}